\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{array}

\title{\textbf{Day-by-Day Work Plan}\\
How Stable Are Regression Conclusions Across Subpopulations?\\
A Finite-Sample Empirical Study}
\author{Project execution schedule}
\date{\today}

\begin{document}

\maketitle

\section{Overview}
This is a compressed work plan for completing the first full draft of the paper under the assumption of approximately \textbf{8 hours of focused work per day}. The plan is designed to produce a strong draft in about \textbf{12 days}, which is aggressive but realistic if the scope is kept disciplined.

\section{Main Objective}
The objective is to complete:
\begin{itemize}
    \item a clear research question,
    \item a short literature review,
    \item a reproducible simulation study,
    \item two real-data case studies,
    \item all main figures and tables,
    \item a full paper draft in LaTeX.
\end{itemize}

\section{Daily Work Structure}
Each day should roughly follow this structure:
\begin{itemize}
    \item \textbf{2 hours:} reading, planning, and note consolidation,
    \item \textbf{4 hours:} coding, computation, experiments, and debugging,
    \item \textbf{2 hours:} writing the paper or documenting results.
\end{itemize}

The most important rule is: \textbf{write every day}. Do not wait until all results are finished.

\section{12-Day Plan}

\subsection*{Day 1: Lock the Scope and the Exact Contribution}
\textbf{Main goal:} finalize the question, paper scope, and contribution.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Write the exact research question in one sentence, starting from the pooled model as the baseline.
    \item Write a short statement of the paper's contribution.
    \item Decide on the 4 simulation scenarios.
    \item Decide on the 4 regression models to compare.
    \item Decide on the 5 main stability metrics:
    \begin{itemize}
        \item sign stability,
        \item standardized coefficient drift,
        \item context-normalized drift,
        \item transported prediction gap,
        \item covariate shift summary.
    \end{itemize}
    \item Set up the project folders:
    \begin{itemize}
        \item \texttt{data/}
        \item \texttt{scripts/}
        \item \texttt{results/}
        \item \texttt{figures/}
        \item \texttt{paper/}
    \end{itemize}
    \item Create the LaTeX paper file and section headings.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item 1-page project memo,
    \item LaTeX skeleton with sections,
    \item clear list of models, metrics, and scenarios.
\end{itemize}

\subsection*{Day 2: Literature Review and Introduction Notes}
\textbf{Main goal:} complete the small literature review and map the introduction.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Read and annotate approximately 6--10 relevant papers.
    \item Take notes on:
    \begin{itemize}
        \item subgroup heterogeneity in regression,
        \item interaction modeling,
        \item transportability / distribution shift,
        \item interpretation versus prediction.
    \end{itemize}
    \item Write a rough introduction outline:
    \begin{itemize}
        \item motivation,
        \item prior work,
        \item gap,
        \item contributions.
    \end{itemize}
    \item Start the bibliography file.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item annotated notes for 6--10 references,
    \item rough introduction draft,
    \item \texttt{references.bib} started.
\end{itemize}

\subsection*{Day 3: Build the Simulation Engine}
\textbf{Main goal:} get one complete simulation pipeline working from start to finish.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Write functions for generating pooled data and subgroup-structured data.
    \item Write functions for fitting:
    \begin{itemize}
        \item pooled OLS,
        \item pooled OLS + group indicator,
        \item pooled OLS + interactions,
        \item subgroup-specific OLS.
    \end{itemize}
    \item Write helper functions to extract:
    \begin{itemize}
        \item coefficient estimates,
        \item signs,
        \item standard errors,
        \item RMSE / MAE.
    \end{itemize}
    \item Run one pooled-baseline scenario end-to-end.
    \item Save outputs in a clean format.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item working simulation script,
    \item one successful end-to-end run,
    \item clear file-saving workflow.
\end{itemize}

\subsection*{Day 4: Implement All Simulation Scenarios}
\textbf{Main goal:} finish the simulation framework for all scenarios.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Implement the 4 main scenarios, starting with the pooled baseline:
    \begin{itemize}
        \item pooled baseline with no heterogeneity,
        \item covariate shift only,
        \item coefficient heterogeneity only,
        \item combined heterogeneity.
    \end{itemize}
    \item Add variation in:
    \begin{itemize}
        \item sample size,
        \item collinearity,
        \item subgroup balance.
    \end{itemize}
    \item Run small pilot batches to test all combinations.
    \item Check for bugs and degenerate fits.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item stable simulation code for all scenarios,
    \item pilot outputs confirming the setup works.
\end{itemize}

\subsection*{Day 5: Run the Full Simulation Study}
\textbf{Main goal:} generate the main simulation results.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Run the full simulation grid.
    \item Save all replicate-level results.
    \item Aggregate outputs into summary tables.
    \item Inspect how the pooled baseline behaves under each scenario:
    \begin{itemize}
        \item sign instability,
        \item standardized coefficient drift,
        \item context-normalized drift,
        \item cross-group prediction deterioration,
        \item covariate shift summary across subgroups.
    \end{itemize}
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item full raw simulation outputs,
    \item first summary tables.
\end{itemize}

\subsection*{Day 6: Create Simulation Figures and Interpret Results}
\textbf{Main goal:} turn the simulation output into interpretable figures and findings.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Create 4--6 core plots, such as:
    \begin{itemize}
        \item sign stability by scenario,
        \item standardized coefficient drift by sample size,
        \item context-normalized drift by sample size,
        \item transported prediction gap by scenario,
        \item covariate shift summary by scenario,
        \item pooled versus subgroup coefficient comparison plots.
    \end{itemize}
    \item Choose the best visualizations.
    \item Write bullet-point interpretations under each figure.
    \item Decide which results are the strongest and deserve emphasis.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item final versions of core simulation figures,
    \item notes on the main empirical findings.
\end{itemize}

\subsection*{Day 7: Select and Prepare Real Datasets}
\textbf{Main goal:} choose two real datasets and prepare them for analysis.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Choose two datasets with:
    \begin{itemize}
        \item continuous response,
        \item clear subgroup variable,
        \item multiple predictors.
    \end{itemize}
    \item Clean and preprocess the data.
    \item Define subgroup variables carefully.
    \item Create exploratory tables and plots.
    \item Check sample sizes within each subgroup.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item two analysis-ready datasets,
    \item initial exploratory summaries.
\end{itemize}

\subsection*{Day 8: Run the Real-Data Analyses}
\textbf{Main goal:} complete the real-data modeling and comparisons.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Fit the pooled model first, then all planned models to both datasets.
    \item Compare:
    \begin{itemize}
        \item pooled coefficients,
        \item subgroup-specific coefficients,
        \item interaction terms,
        \item within-group and out-of-group prediction.
    \end{itemize}
    \item Build 2--4 real-data tables/figures.
    \item Write down how the real-data findings support or contrast with the simulation findings.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item completed real-data analyses,
    \item draft figures/tables for Section 4.
\end{itemize}

\subsection*{Day 9: Write the Methods Section}
\textbf{Main goal:} fully draft the methods section.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Write the notation and problem setup.
    \item Define the models clearly.
    \item Define the stability metrics mathematically.
    \item Describe the simulation design.
    \item Describe the real-data analysis workflow.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item full draft of the Methods section.
\end{itemize}

\subsection*{Day 10: Write the Simulation Results Section}
\textbf{Main goal:} write the strongest section of the paper.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Insert the simulation figures and tables into LaTeX.
    \item Write the narrative for each scenario.
    \item Highlight the major patterns:
    \begin{itemize}
        \item when pooled models fail,
        \item when interaction models help,
        \item when prediction remains stable but interpretation does not.
    \end{itemize}
    \item Keep interpretation tied directly to the research questions.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item full draft of the Simulation Results section.
\end{itemize}

\subsection*{Day 11: Write the Introduction and Real-Data Section}
\textbf{Main goal:} draft the remaining core sections.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Write the Introduction:
    \begin{itemize}
        \item motivation,
        \item literature review,
        \item gap,
        \item contributions.
    \end{itemize}
    \item Write the real-data section.
    \item Make sure the introduction promises only what the paper actually delivers.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item draft Introduction,
    \item draft Real-Data section.
\end{itemize}

\subsection*{Day 12: Write Discussion, Conclusion, Abstract, and Polish}
\textbf{Main goal:} complete the first full draft.

\textbf{Tasks:}
\begin{enumerate}[label=(\arabic*)]
    \item Write the Discussion:
    \begin{itemize}
        \item main findings,
        \item practical implications,
        \item limitations,
        \item future work.
    \end{itemize}
    \item Write the Conclusion.
    \item Write the Abstract last.
    \item Clean the references.
    \item Check notation consistency.
    \item Improve figure captions.
    \item Proofread the full document once from beginning to end.
\end{enumerate}

\textbf{Deliverables by end of day:}
\begin{itemize}
    \item complete first full draft of the paper.
\end{itemize}

\section{Optional Days 13--14 for Buffer and Revision}
If possible, reserve two extra days for revision.

\subsection*{Day 13: Technical Revision}
\begin{itemize}
    \item Re-run any unstable analyses.
    \item Simplify any overloaded sections.
    \item Remove weak figures or unnecessary tables.
    \item Tighten the claims to match the evidence.
\end{itemize}

\subsection*{Day 14: Writing Revision}
\begin{itemize}
    \item Improve clarity and flow.
    \item Shorten repetitive paragraphs.
    \item Make the introduction sharper.
    \item Make sure the conclusion is specific and not generic.
\end{itemize}

\section{Checklist of Key Deliverables}
By the end of the schedule, you should have:
\begin{enumerate}[label=(\arabic*)]
    \item a working bibliography,
    \item a complete LaTeX manuscript,
    \item a simulation pipeline in R,
    \item two real-data analyses,
    \item 4--6 high-quality figures,
    \item 2--4 summary tables,
    \item one full draft ready for feedback.
\end{enumerate}

\section{Priority Order if You Fall Behind}
If you fall behind schedule, prioritize in this order:
\begin{enumerate}[label=(\arabic*)]
    \item finish the simulation study,
    \item complete the methods and simulation results writing,
    \item include only two real datasets,
    \item reduce the number of figures,
    \item postpone optional extensions.
\end{enumerate}

\section{Final Advice}
The paper will be strongest if it remains narrow, empirical, and clear. The simulation study should carry the paper, while the real-data examples should support and illustrate the main message. The goal is not to solve all of subgroup heterogeneity or all of transportability. The goal is to produce a clean, credible empirical paper with a precise question and strong execution.

\end{document}